Topology and physical distinguishability

### 2017-07-12 Articles/TopologyAndExperimentalDistinguishability/article.tex
Fix typos in Conclusion

We have shown that it is possible to formally capture the requirements of experimental sciences using experimental observations and their properties. These definitions lead naturally to topological spaces giving the result that any set of experimentally distinguishable possibilities is a Hausdorf and second-countable topological space. In the same framework, experimental relationships between these objects are represented mathematically by continuous functions and are themselves experimentally distinguishable objects as they too can be given a Hausdorf and secound-countable topology. The ability to create functions of any order confirms that the universe of discourse provided by these definition is closed and self-consistent.

>>>>

We have shown that it is possible to formally capture the requirements of experimental sciences using experimental observations and their properties. These definitions lead naturally to topological spaces, giving the result that any set of experimentally distinguishable possibilities is a Hausdorff and second-countable topological space. In the same framework, experimental relationships between these objects are represented mathematically by continuous functions and are themselves experimentally distinguishable objects, as they too can be given a Hausdorff and secound-countable topology. The ability to create functions of any order confirms that the universe of discourse provided by these definitions is closed and self-consistent.
